The hydra and the rooster

### 2020-07-14 latex/chapter-ordinals.tex
Limits_and_Successors now autonomous

@@

\begin{Coqsrc}
Definition succ (alpha : t) := match alpha with
                                 inl i => inl (S i)
                               | inr i => inr (S i)
                               end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition succb (alpha: t) := match alpha with
                                   inr (S  _) | inl (S _) => true
                                 | _ => false
                                 end.
\end{Coqsrc}

\begin{Coqsrc}
Lemma succb_correct alpha : succb alpha <-> exists beta,  alpha = succ beta.
\end{Coqsrc}

\begin{Coqsrc}
Definition limitb (alpha : t) := match alpha with
                                     (inr 0) => true
                                   | _ => false
                                   end.
\end{Coqsrc}

\begin{Coqsrc}
Lemma omega_is_limit:
   Omega_limit fin omega.
Proof.
  split.
  - constructor.
  - inversion_clear  1.
    + exists (S x); constructor; auto with arith.
    + lia.
Qed.
\end{Coqsrc}

>>>>

\begin{todo}
  Well foundedness; instance of OrdinalNotation.
\end{todo}

@@

\subsubsection{Computing successors}

The following function computes the successor of any ordinal less than $\omega+\omega$, by a simple pattern matching.

\begin{Coqsrc}
Definition succ (alpha : t) := match alpha with
                                 inl i => inl (S i)
                               | inr i => inr (S i)
                               end.

Compute succ omega.
\end{Coqsrc}

\begin{Coqanswer}
  = inr 1
     : nat + nat
\end{Coqanswer}

\begin{Coqsrc}
Lemma lt_succ alpha : alpha < succ alpha.
Proof.
 destruct alpha; constructor; auto with arith. 
Qed.
\end{Coqsrc}

The correctness  of the \texttt{succ} function is asserted by the following lemma.

@@

Being a successor is decidable, thanks to the following boolean function.

\begin{Coqsrc}
Definition succb (alpha: t) := match alpha with
                                   inr (S  _) | inl (S _) => true
                                 | _ => false
                                 end.

Lemma succb_correct alpha : succb alpha <-> exists beta,  alpha = succ beta.
\end{Coqsrc}

\subsubsection{Deciding whether a given ordinal is a limit}

In the same way as successors, one can decide by pattern matching wether a given ordinal (dont' forget less than $\omega+\omega$ !) is a limit.

\begin{Coqsrc}
Definition limitb (alpha : t) := match alpha with
                                     (inr 0) => true
                                   | _ => false
                                   end.

Lemma limitb_correct alpha  : limitb alpha <-> 
                              exists s: nat -> t, Omega_limit s alpha.
\end{Coqsrc}
